---
title: "Body Weight and Length - F0"
author: "Hamza"
date: "1 June 2019"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)

# Load custom functions
source("../Scripts/functions_learning.R")
source("../Scripts/functions_repeatability.R")

#Run this after all the coding has been run with 10,000 bootstraps
save.image(file='myEnvironment.RData') 
#load('myEnvironment.RData')
```

#Import and filter data
```{r, include = FALSE}
#Master file with raw data
Data <- read.csv("../Data/Weight_Length/Analysis.csv")

#Filtered to ensure no spare tanks or fish are included in the analysis
Data_subset = filter(Data, Tank %in% c("HA_C1","HA_C2","HA_C3", "HA_C4", "HA_T1","HA_T2","HA_T3","HA_T4"))
Weight_Length_Data = filter(Data_subset, !Fish_ID %in% c("a6834","a6923","a7226","a7070","a7250","a7336","a7600","a7573","a7660","a6929","a6990","a7407","a7090","a7286","a7539","a6884","a7206","a7488","a6846","a7560","a7495","a7649","a7604","a7015","a7253","a7610","a7566","a7719","a7682","a7266","a7494","a7548","a7207"))

#Subsetted data for later comparison of week 0 and final week
Week_0 <- subset(Weight_Length_Data, Weight_Length_Data$Week == "0")
Week_22 <- subset(Weight_Length_Data, Weight_Length_Data$Week == "22")

#Subseting data by control and treatment
Weight_Length_Control <- subset(Weight_Length_Data, Weight_Length_Data$Treatment_Tank == "Control") 
Weight_Length_Treatment <- subset(Weight_Length_Data, Weight_Length_Data$Treatment_Tank == "Treatment") 
```

### REPEATABILITY ANALYSIS FOR BODY WEIGHT AND LENGTH 
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION (FOR BOTH CONTROL AND TREATMENT)
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITIES
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT GROUPS

# Body Weight
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_Body_Weight <- lmer(Weight.g. ~ Treatment_Tank + Sex + Week + (1 | Fish_ID), data = Weight_Length_Data) #mixed model 
tab_model(Model_Body_Weight)
hist(residuals(Model_Body_Weight))#histogram of residuals to check for normal distribution 

Model_Body_Weight2 <- lmer(Weight.g. ~ Treatment_Tank*Week + Sex*Week + (1 | Fish_ID) + (1 + Week|Tank), data = Weight_Length_Data) 
summary(Model_Body_Weight2)
tab_model(Model_Body_Weight2)
hist(residuals(Model_Body_Weight2))



#Calculating repeatabilities (without week and with week)
rpt_weight(Weight_Length_Control) -> rpt_body_weight_control #without week factored in

rpt_weight(Weight_Length_Treatment) -> rpt_body_weight_treatment #without week factored in

rpt_weight2(Weight_Length_Control) -> rpt_body_weight_control2 #adjusted for week

rpt_weight2(Weight_Length_Treatment) -> rpt_body_weight_treatment2 #adjusted for week


#Obtaining within-individual and between-individual variance for body weight

rpt_within_weight(Weight_Length_Control) -> within_between_body_weight_control
rpt_within_weight(Weight_Length_Treatment) -> within_between_body_weight_treatment

rpt_within_weight2(Weight_Length_Control) -> within_between_body_weight_control2 #adjusted for week
rpt_within_weight2(Weight_Length_Treatment) -> within_between_body_weight_treatment2 #adjusted for week


#Obtaining differences between repeatabilities using custom made functions
Control_weight_boot <- unlist_rptr(rpt_body_weight_control) 
Treatment_weight_boot <- unlist_rptr(rpt_body_weight_treatment) 
body_weight_diff <- difference_boot(Control_weight_boot,Treatment_weight_boot) #calculating the difference
q_body_weight <- quantiles_diff_boot(body_weight_diff) #obtaining 95% CI
m_mody_weight <- mean(body_weight_diff) #Obtaining mean

q_body_weight
m_mody_weight

# Calculating difference in variance between control and treatment group 
Model_Weight_1 <- lme(Weight.g. ~ (Treatment_Tank + Sex + Week)^2, random = ~ 1| Fish_ID, data = Weight_Length_Data) #Mixed model without variance structure
summary(Model_Weight_1)
Model_Weight_2 <- lme(Weight.g. ~ (Treatment_Tank + Sex + Week)^2, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Treatment_Tank), data = Weight_Length_Data) #mixed model with variance structure varIdent
summary(Model_Weight_2)
anova(Model_Weight_1, Model_Weight_2) #calculating difference between two models to find difference in variance
```

# Body Length 
```{r, echo=FALSE}

#Check Normality with mixed model and then histogram of residuals

Model_Body_Length <- lmer(Fish_Length_cm ~ Treatment_Tank + Sex + Week + (1 | Fish_ID), data = Weight_Length_Data) #mixed model 
tab_model(Model_Body_Length)
hist(residuals(Model_Body_Length))#histogram of residuals to check for normal distribution 

Model_Body_Length2 <- lmer(Fish_Length_cm ~ Treatment_Tank + Sex + Week + (1 | Fish_ID) + (1 + Week|Tank), data = Weight_Length_Data) 
summary(Model_Body_Length2)
tab_model(Model_Body_Length2)
hist(residuals(Model_Body_Length2))



#Calculating repeatabilities using custom made functions
rpt_length2(Weight_Length_Control) -> rpt_length_control
rpt_length_control
rpt_length2(Weight_Length_Treatment) -> rpt_length_treatment
rpt_length_treatment

#Obtaining within-individual and between-individual variance for body weight

rpt_within_length(Weight_Length_Control) -> within_between_body_length_control
rpt_within_length(Weight_Length_Treatment) -> within_between_body_length_treatment

#Obtaining differences between repeatabilities using custom made functions
Control_length_boot <- unlist_rptr(rpt_body_weight_control) 
Treatment_length_boot <- unlist_rptr(rpt_body_weight_treatment) 
body_length_diff <- difference_boot(Control_length_boot,Treatment_length_boot) #calculating the difference
q_body_length <- quantiles_diff_boot(body_length_diff) #obtaining 95% CI
m_mody_length <- mean(body_length_diff) #Obtaining mean

q_body_length
m_mody_length

# Calculating difference in variance between control and treatment group 
Model_Length_1 <- lme(Fish_Length_cm ~ Treatment_Tank*Week + Sex*Week, random = ~ 1| Fish_ID, data = Weight_Length_Data) #Mixed model without variance structure
summary(Model_Length_1)
Model_Length_2 <- lme(Fish_Length_cm ~ Treatment_Tank*Week + Sex*Week, random = ~ 1| Fish_ID, weights = varIdent(form=~1|Treatment_Tank), data = Weight_Length_Data) #mixed model with variance structure varIdent
summary(Model_Length_2)
anova(Model_Length_1, Model_Length_2) #calculating difference between two models to find difference in variance
```


# Visualizations
Boxplot to show distribution at beginning of the experiment and at the end of the experiment
```{r, echo = FALSE}
boxplot_0 <- ggplot(data = Week_0) +
  geom_boxplot(mapping = aes(x = Treatment_Tank, y = Weight.g., fill = Treatment_Tank)) +
  facet_grid(~Sex)
  
boxplot_0

boxplot_22 <- ggplot(data = Week_22) +
  geom_boxplot(mapping = aes(x = Treatment_Tank, y = Weight.g., fill = Treatment_Tank)) +
  facet_grid(~Sex)
  
boxplot_22

```  

# Mixed Models to account for week 0
```{r, echo = FALSE}
Weight_Model <- lmer(Weight.g. ~ Treatment_Tank + Week + Sex + (1|Fish_ID), data=Data)
tab_model(Weight_Model)

Weight_Model <- lmer(Weight.g. ~ Treatment_Tank*Week + Sex + (1|Fish_ID), data=Data)
tab_model(Weight_Model)

Weight_Model <- lmer(Weight.g. ~ Treatment_Tank*Week + Sex*Week  + (1|Fish_ID) + (1 + Week|Tank), data=Data)
tab_model(Weight_Model)

#A significant interaction exists between treatment and week as well as sex and week. What this means is that the treatment and control tanks have a different slope and this is also dependent on the week. This is also the case for the sexes, with the females having a steeper slope, also significantly different by the week. 


Weight_Model <- lmer(Fish_Length_cm ~ Treatment_Tank*Week + Sex*Week  + (1|Fish_ID) + (1 + Week|Tank), data=Data)
tab_model(Weight_Model)

model_week0_weight <- lmer(Weight.g. ~ Treatment_Tank + Sex + Fish_Length_cm + (1|Tank), data = Week_0 )
tab_model(model_week0_weight)

model_week0_length <- lmer(Fish_Length_cm ~ Treatment_Tank + Sex + (1|Tank), data = Week_0 )
tab_model(model_week0_length)


model_week0_bmi <- lmer(scale(BMI) ~ Treatment_Tank + Sex + (1|Tank), data = Week_0 )
tab_model(model_week0_bmi)

lm_week0 <- glm(scale(BMI) ~ Treatment_Tank + Sex , data = Week_0 )
tab_model(lm_week0)


lm_week0 <- glm(Weight.g. ~ Treatment_Tank + Sex , data = Week_0 )
tab_model(lm_week0)

lm_week0 <- glm(Fish_Length_cm ~ Treatment_Tank + Sex , data = Week_0 )
tab_model(lm_week0)

```


# Line plot (body weight)

```{r, echo = FALSE}
Summary_Weight <- summarySE(Weight_Length_Data, measurevar="Weight.g.", groupvars=c("Week","Treatment_Tank", "Sex"))

# So error bars aren't overlapping, we can use this:
pd <- position_dodge(0.1) # move them .05 to the left and right


line_plot_weight <- ggplot(Summary_Weight, aes(x=Week, y=Weight.g., colour=Treatment_Tank)) + 
    geom_errorbar(aes(ymin=Weight.g.-se, ymax=Weight.g.+se), colour="black", width=.1, position=pd) +
    geom_line(position=pd) +
    geom_point(position=pd, size=3) +
  labs(title = "Obesogenic vs. Control Diet",
              subtitle = "Weight change after 22 weeks") +
  facet_grid(~Sex)

line_plot_weight


```









# Line plot (fish length) for tanks

```{r, echo = FALSE}
Summary_Length <- summarySE(Weight_Length_Data, measurevar="Fish_Length_cm", groupvars=c("Week","Treatment_Tank", "Sex"))

# So error bars aren't overlapping, we can use this:
pd <- position_dodge(0.1) # move them .05 to the left and right

plot_fish_length_tanks <- ggplot(Summary_Length, aes(x=Week, y=Fish_Length_cm, colour=Treatment_Tank)) + 
  geom_errorbar(aes(ymin=Fish_Length_cm-se, ymax=Fish_Length_cm+se),colour="black", width=.1, position=pd) +
  geom_line(position=pd) +
  geom_point(position=pd)+
  labs(title = "Obesogenic vs. Control Diet",
              subtitle = "Fish lengths after 22 weeks") +
  facet_grid(~Sex)
          

plot_fish_length_tanks


```

#Summary (BMI)

```{r, echo = FALSE}

Summary_BMI <- summarySE(Weight_Length_Data, measurevar="BMI", groupvars=c("Week","Treatment_Tank", "Sex"))


plot_bmi <- ggplot(Summary_BMI, aes(x=Week, y=BMI, colour=Treatment_Tank)) + 
  geom_errorbar(aes(ymin=BMI-se, ymax=BMI+se), width=.1,colour="black", position=pd) +
  geom_line(position=pd) +
  labs(title = "Obesogenic vs. Control Diet",
              subtitle = "Fish BMI after 22 weeks (g/cm2)")+
  facet_grid(~Sex)

          

plot_bmi


```




```{r}
#Making scatterplot

Scatterplot <- ggplot(Weight_Length_Data, aes(Week, Weight.g., colour = Treatment_Tank)) +
  geom_jitter() +
  theme_bw() +
  facet_grid(~Sex) +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), aes(fill = Treatment_Tank)) #try different formulas and compare against each other
Scatterplot



```

