---
title: "F0 Anxiety Plots"
author: "Hamza"
date: "23/10/2020"
output: html_document
---

### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)
# Load custom functions
source("../Scripts/functions_plots.R") #load custom functions
```


#Creating tibbles to use in plotting repeatabilities : one for overall plots, and one for sex plots

Total distance F0
```{r, echo=FALSE}
Tot_Dist_rptr_F0 <- tibble(
  Group = c("Control", "Treatment", "Contrast", "Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_Tot_Dist$R$Fish_ID,Treatment_Tot_Dist$R$Fish_ID, m1, within_between_tot_dist_control$R[1], within_between_tot_dist_control$R[2],within_between_tot_dist_treatment$R[1], within_between_tot_dist_treatment$R[2]),
  ci.lb = c(Control_Tot_Dist$CI_emp$`2.5%`,Treatment_Tot_Dist$CI_emp$`2.5%`,-0.10, within_between_tot_dist_control$CI_emp[1,1], within_between_tot_dist_control$CI_emp[2,1],within_between_tot_dist_treatment$CI_emp[1,1], within_between_tot_dist_treatment$CI_emp[2,1]),
  ci.ub = c(Control_Tot_Dist$CI_emp$`97.5%`,Treatment_Tot_Dist$CI_emp$`97.5%`, 0.24, within_between_tot_dist_control$CI_emp[1,2], within_between_tot_dist_control$CI_emp[2,2],within_between_tot_dist_treatment$CI_emp[1,2], within_between_tot_dist_treatment$CI_emp[2,2]),
Endpoint = c("Total distance", "Total distance", "Total distance", "Total distance", "Total distance","Total distance","Total distance"))
  
Tot_Dist_rptr_F0$r <- as.numeric(Tot_Dist_rptr_F0$r)
Tot_Dist_rptr_F0

Tot_Dist_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_Tot_Dist_Male$R$Fish_ID,Control_Tot_Dist_Female$R$Fish_ID,Treatment_Tot_Dist_Male$R$Fish_ID,Treatment_Tot_Dist_Female$R$Fish_ID,mean_tot_Control, mean_tot_Treatment ),
  ci.lb = c(Control_Tot_Dist_Male$CI_emp$`2.5%`,Control_Tot_Dist_Female$CI_emp$`2.5%`,Treatment_Tot_Dist_Male$CI_emp$`2.5%`,Treatment_Tot_Dist_Female$CI_emp$`2.5%`, -0.04, -0.10),
  ci.ub = c(Control_Tot_Dist_Male$CI_emp$`97.5%`,Control_Tot_Dist_Female$CI_emp$`97.5%`,Treatment_Tot_Dist_Male$CI_emp$`97.5%`,Treatment_Tot_Dist_Female$CI_emp$`97.5%`, 0.40, 0.38),
Endpoint = c("Total distance","Total distance","Total distance","Total distance","Total distance","Total distance"))
  
Tot_Dist_rptr_sex
```


#Time spent in the low zone 

```{r}
low_dur_rptr <- tibble(
  Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)" ),
  r = c(Control_low_dur$R$Fish_ID,Treatment_low_dur$R$Fish_ID, m2,within_between_low_dur_control$R[1], within_between_low_dur_control$R[2],within_between_low_dur_treatment$R[1], within_between_low_dur_treatment$R[2]),
  ci.lb = c(Control_low_dur$CI_emp$`2.5%`,Treatment_low_dur$CI_emp$`2.5%`, -0.21,within_between_low_dur_control$CI_emp[1,1], within_between_low_dur_control$CI_emp[2,1],within_between_low_dur_treatment$CI_emp[1,1], within_between_low_dur_treatment$CI_emp[2,1]),
  ci.ub = c(Control_low_dur$CI_emp$`97.5%`,Treatment_low_dur$CI_emp$`97.5%`, 0.23,within_between_low_dur_control$CI_emp[1,2], within_between_low_dur_control$CI_emp[2,2],within_between_low_dur_treatment$CI_emp[1,2], within_between_low_dur_treatment$CI_emp[2,2] ),
Endpoint = c("Time spent in low zone", "Time spent in low zone", "Time spent in low zone","Time spent in low zone","Time spent in low zone","Time spent in low zone","Time spent in low zone"))

low_dur_rptr$r <- as.numeric(low_dur_rptr$r)
low_dur_rptr



low_dur_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_low_dur_Male$R$Fish_ID,Control_low_dur_Female$R$Fish_ID,Treatment_low_dur_Male$R$Fish_ID,Treatment_low_dur_Female$R$Fish_ID,mean_low_dur_Control,mean_low_dur_Treatment),
  ci.lb = c(Control_low_dur_Male$CI_emp$`2.5%`,Control_low_dur_Female$CI_emp$`2.5%`,Treatment_low_dur_Male$CI_emp$`2.5%`,Treatment_low_dur_Female$CI_emp$`2.5%`,-0.28,-0.04),
  ci.ub = c(Control_low_dur_Male$CI_emp$`97.5%`,Control_low_dur_Female$CI_emp$`97.5%`,Treatment_low_dur_Male$CI_emp$`97.5%`,Treatment_low_dur_Female$CI_emp$`97.5%`,0.26,0.48),
Endpoint = c("Time spent in low zone","Time spent in low zone","Time spent in low zone","Time spent in low zone","Time spent in low zone","Time spent in low zone"))

low_dur_rptr_sex
```

Time spent in mid zone
```{r, echo=FALSE}
mid_dur_rptr <- tibble(
  Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)", "Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_mid_dur$R$Fish_ID,Treatment_mid_dur$R$Fish_ID, m3,within_between_mid_dur_control$R[1], within_between_mid_dur_control$R[2],within_between_mid_dur_treatment$R[1], within_between_mid_dur_treatment$R[2]),
  ci.lb = c(Control_mid_dur$CI_emp$`2.5%`,Treatment_mid_dur$CI_emp$`2.5%`, -0.09,within_between_mid_dur_control$CI_emp[1,1], within_between_mid_dur_control$CI_emp[2,1],within_between_mid_dur_treatment$CI_emp[1,1], within_between_mid_dur_treatment$CI_emp[2,1]),
  ci.ub = c(Control_mid_dur$CI_emp$`97.5%`,Treatment_mid_dur$CI_emp$`97.5%`,0.29,within_between_mid_dur_control$CI_emp[1,2], within_between_mid_dur_control$CI_emp[2,2],within_between_mid_dur_treatment$CI_emp[1,2], within_between_mid_dur_treatment$CI_emp[2,2]),
Endpoint = c("Time spent in mid zone", "Time spent in mid zone", "Time spent in mid zone","Time spent in mid zone","Time spent in mid zone","Time spent in mid zone","Time spent in mid zone"))

mid_dur_rptr$r <- as.numeric(mid_dur_rptr$r)  
mid_dur_rptr

mid_dur_rptr$r <- as.numeric(mid_dur_rptr$r)

mid_dur_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_mid_dur_Male$R$Fish_ID,Control_mid_dur_Female$R$Fish_ID,Treatment_mid_dur_Male$R$Fish_ID,Treatment_mid_dur_Female$R$Fish_ID,mean_mid_dur_control,mean_mid_dur_Treatment),
  ci.lb = c(Control_mid_dur_Male$CI_emp$`2.5%`,Control_mid_dur_Female$CI_emp$`2.5%`,Treatment_mid_dur_Male$CI_emp$`2.5%`,Treatment_mid_dur_Female$CI_emp$`2.5%`,-0.11,-0.26),
  ci.ub = c(Control_mid_dur_Male$CI_emp$`97.5%`,Control_mid_dur_Female$CI_emp$`97.5%`,Treatment_mid_dur_Male$CI_emp$`97.5%`,Treatment_mid_dur_Female$CI_emp$`97.5%`,0.37,0.30),
Endpoint = c("Time spent in mid zone","Time spent in mid zone","Time spent in mid zone","Time spent in mid zone","Time spent in mid zone","Time spent in mid zone"))

mid_dur_rptr_sex
```

Time spent in the high zone
```{r, echo=FALSE}
high_dur_rptr <- tibble(
  Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_high_dur$R$Fish_ID,Treatment_high_dur$R$Fish_ID, m4,within_between_high_dur_control$R[1], within_between_high_dur_control$R[2],within_between_high_dur_treatment$R[1], within_between_high_dur_treatment$R[2]),
  ci.lb = c(Control_high_dur$CI_emp$`2.5%`,Treatment_high_dur$CI_emp$`2.5%`, -0.19,within_between_high_dur_control$CI_emp[1,1], within_between_high_dur_control$CI_emp[2,1],within_between_high_dur_treatment$CI_emp[1,1], within_between_high_dur_treatment$CI_emp[2,1]),
  ci.ub = c(Control_high_dur$CI_emp$`97.5%`,Treatment_high_dur$CI_emp$`97.5%`, 0.22, within_between_high_dur_control$CI_emp[1,2], within_between_high_dur_control$CI_emp[2,2],within_between_high_dur_treatment$CI_emp[1,2], within_between_high_dur_treatment$CI_emp[2,2]),
Endpoint = c("Time spent in high zone", "Time spent in high zone", "Time spent in high zone","Time spent in high zone","Time spent in high zone","Time spent in high zone","Time spent in high zone"))

high_dur_rptr$r <- as.numeric(high_dur_rptr$r)  
high_dur_rptr



high_dur_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_high_dur_Male$R$Fish_ID,Control_high_dur_Female$R$Fish_ID,Treatment_high_dur_Male$R$Fish_ID,Treatment_high_dur_Female$R$Fish_ID,mean_high_dur_control,mean_high_dur_Treatment ),
  ci.lb = c(Control_high_dur_Male$CI_emp$`2.5%`,Control_high_dur_Female$CI_emp$`2.5%`,Treatment_high_dur_Male$CI_emp$`2.5%`,Treatment_high_dur_Female$CI_emp$`2.5%`,-0.14,0.01),
  ci.ub = c(Control_high_dur_Male$CI_emp$`97.5%`,Control_high_dur_Female$CI_emp$`97.5%`,Treatment_high_dur_Male$CI_emp$`97.5%`,Treatment_high_dur_Female$CI_emp$`97.5%`,0.32,0.53),
Endpoint = c("Time spent in high zone","Time spent in high zone","Time spent in high zone","Time spent in high zone","Time spent in high zone","Time spent in high zone"))

high_dur_rptr_sex
```


Freezing duration
```{r, echo=FALSE}
freezing_dur_rptr <- tibble(
  Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_freezing_dur$R$Fish_ID,Treatment_freezing_dur$R$Fish_ID, m5, within_between_freezing_dur_control$R[1], within_between_freezing_dur_control$R[2],within_between_freezing_dur_treatment$R[1], within_between_freezing_dur_treatment$R[2]),
  ci.lb = c(Control_freezing_dur$CI_emp$`2.5%`,Treatment_freezing_dur$CI_emp$`2.5%`, -0.18, within_between_freezing_dur_control$CI_emp[1,1], within_between_freezing_dur_control$CI_emp[2,1],within_between_freezing_dur_treatment$CI_emp[1,1], within_between_freezing_dur_treatment$CI_emp[2,1]),
  ci.ub = c(Control_freezing_dur$CI_emp$`97.5%`,Treatment_freezing_dur$CI_emp$`97.5%`, 0.20,within_between_freezing_dur_control$CI_emp[1,2], within_between_freezing_dur_control$CI_emp[2,2],within_between_freezing_dur_treatment$CI_emp[1,2], within_between_freezing_dur_treatment$CI_emp[2,2]),
Endpoint = c("Time spent freezing", "Time spent freezing", "Time spent freezing","Time spent freezing","Time spent freezing","Time spent freezing","Time spent freezing"))
  
freezing_dur_rptr

freezing_dur_rptr$r <- as.numeric(freezing_dur_rptr$r)

freezing_dur_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_freezing_dur_Male$R$Fish_ID,Control_freezing_dur_Female$R$Fish_ID,Treatment_freezing_dur_Male$R$Fish_ID,Treatment_freezing_dur_Female$R$Fish_ID,mean_freezing_dur_control,mean_freezing_dur_Treatment),
  ci.lb = c(Control_freezing_dur_Male$CI_emp$`2.5%`,Control_freezing_dur_Female$CI_emp$`2.5%`,Treatment_freezing_dur_Male$CI_emp$`2.5%`,Treatment_freezing_dur_Female$CI_emp$`2.5%`,-0.05,-0.22),
  ci.ub = c(Control_freezing_dur_Male$CI_emp$`97.5%`,Control_freezing_dur_Female$CI_emp$`97.5%`,Treatment_freezing_dur_Male$CI_emp$`97.5%`,Treatment_freezing_dur_Female$CI_emp$`97.5%`,0.42,0.30),
Endpoint = c("Time spent freezing","Time spent freezing","Time spent freezing","Time spent freezing","Time spent freezing","Time spent freezing"))

freezing_dur_rptr_sex
```

Entries into high zone
```{r}
frequency_rptr <- tibble(
  Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_freq_high$R$Fish_ID,Treatment_freq_high$R$Fish_ID, m7,within_between_freq_high_control$R[1], within_between_freq_high_control$R[2],within_between_freq_high_treatment$R[1], within_between_freq_high_treatment$R[2]),
  ci.lb = c(Control_freq_high$CI_emp$`2.5%`,Treatment_freq_high$CI_emp$`2.5%`, -0.12,within_between_freq_high_control$CI_emp[1,1], within_between_freq_high_control$CI_emp[2,1],within_between_freq_high_treatment$CI_emp[1,1], within_between_freq_high_treatment$CI_emp[2,1]),
  ci.ub = c(Control_freq_high$CI_emp$`97.5%`,Treatment_freq_high$CI_emp$`97.5%`, 0.23,within_between_freq_high_control$CI_emp[1,2], within_between_freq_high_control$CI_emp[2,2],within_between_freq_high_treatment$CI_emp[1,2], within_between_freq_high_treatment$CI_emp[2,2]),
Endpoint = c("Entries into high zone", "Entries into high zone", "Entries into high zone","Entries into high zone","Entries into high zone","Entries into high zone","Entries into high zone"))

frequency_rptr$r <- as.numeric(frequency_rptr$r)  
frequency_rptr

frequency_rptr$r <- as.numeric(frequency_rptr$r)

freq_high_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_freq_high_Male$R$Fish_ID,Control_freq_high_Female$R$Fish_ID,Treatment_freq_high_Male$R$Fish_ID,Treatment_freq_high_Female$R$Fish_ID,mean_freq_high_control,mean_freq_high_Treatment),
  ci.lb = c(Control_freq_high_Male$CI_emp$`2.5%`,Control_freq_high_Female$CI_emp$`2.5%`,Treatment_freq_high_Male$CI_emp$`2.5%`,Treatment_freq_high_Female$CI_emp$`2.5%`,-0.28,-0.16),
  ci.ub = c(Control_freq_high_Male$CI_emp$`97.5%`,Control_freq_high_Female$CI_emp$`97.5%`,Treatment_freq_high_Male$CI_emp$`97.5%`,Treatment_freq_high_Female$CI_emp$`97.5%`,0.37,0.40),
Endpoint = c("Entries into high zone","Entries into high zone","Entries into high zone","Entries into high zone","Entries into high zone","Entries into high zone"))

freq_high_rptr_sex
```


Latency to high
```{r}
latency_rptr <- tibble(
 Group = c("Control", "Treatment", "Contrast","Between-Individual Variance (Control Group)", "Within-Individual Variance (Control Group)","Between-Individual Variance (Treatment Group)", "Within-Individual Variance (Treatment Group)"),
  r = c(Control_latency_high$R$Fish_ID,Treatment_latency_high$R$Fish_ID, m6,within_between_latency_high_control$R[1], within_between_latency_high_control$R[2],within_between_latency_high_treatment$R[1], within_between_latency_high_treatment$R[2]),
  ci.lb = c(Control_latency_high$CI_emp$`2.5%`,Treatment_latency_high$CI_emp$`2.5%`, 0.01,within_between_latency_high_control$CI_emp[1,1], within_between_latency_high_control$CI_emp[2,1],within_between_latency_high_treatment$CI_emp[1,1], within_between_latency_high_treatment$CI_emp[2,1]),
  ci.ub = c(Control_latency_high$CI_emp$`97.5%`,Treatment_latency_high$CI_emp$`97.5%`, 0.57,within_between_latency_high_control$CI_emp[1,2], within_between_latency_high_control$CI_emp[2,2],within_between_latency_high_treatment$CI_emp[1,2], within_between_latency_high_treatment$CI_emp[2,2]),
Endpoint = c("Latency to high zone", "Latency to high zone", "Latency to high zone","Latency to high zone","Latency to high zone","Latency to high zone","Latency to high zone"))


latency_rptr$r <- as.numeric(latency_rptr$r)
latency_rptr

latency_rptr$r <- as.numeric(latency_rptr$r)

latency_high_rptr_sex <- tibble(
  Tank = c("Control","Control", "Treatment", "Treatment", "Control", "Treatment"),
  Condition = c("Male","Female","Male", "Female", "Contrast", "Contrast"),
  r = c(Control_latency_high_Male$R$Fish_ID,Control_latency_high_Female$R$Fish_ID,Treatment_latency_high_Male$R$Fish_ID,Treatment_latency_high_Female$R$Fish_ID,mean_latency_high_control,mean_latency_high_Treatment),
  ci.lb = c(Control_latency_high_Male$CI_emp$`2.5%`,Control_latency_high_Female$CI_emp$`2.5%`,Treatment_latency_high_Male$CI_emp$`2.5%`,Treatment_latency_high_Female$CI_emp$`2.5%`,-0.35,-0.26),
  ci.ub = c(Control_latency_high_Male$CI_emp$`97.5%`,Control_latency_high_Female$CI_emp$`97.5%`,Treatment_latency_high_Male$CI_emp$`97.5%`,Treatment_latency_high_Female$CI_emp$`97.5%`,0.63,0.39),
Endpoint = c("Latency to high zone","Latency to high zone","Latency to high zone","Latency to high zone","Latency to high zone","Latency to high zone"))

latency_high_rptr_sex
```

Joining tibbles to use in plotting 
```{r}

#Joining all tibbles for overall
Overall_Data_Joined1 <- full_join(Tot_Dist_rptr_F0, low_dur_rptr)
Overall_Data_Joined2 <- full_join(Overall_Data_Joined1, mid_dur_rptr)
Overall_Data_Joined3 <- full_join(Overall_Data_Joined2, high_dur_rptr)
Overall_Data_Joined4 <- full_join(Overall_Data_Joined3, freezing_dur_rptr)
Overall_Data_Joined5 <- full_join(Overall_Data_Joined4, frequency_rptr)
Overall_Anxiety_Data_Joined_Full_F0 <- full_join(Overall_Data_Joined5, latency_rptr)


Overall_Anxiety_Plotting_Data_F0 <- subset(Overall_Anxiety_Data_Joined_Full_F0, Overall_Anxiety_Data_Joined_Full_F0$Group %in% c("Treatment","Control","Contrast"))

Overall_Anxiety_Plotting_Data_F0 #Will be used for plotting just the overall repeatabilites for tall tank, short tank and the contrast



#Joining all tibbles for sex
Overall_Data_Joined11 <- full_join(Tot_Dist_rptr_sex, low_dur_rptr_sex)
Overall_Data_Joined22 <- full_join(Overall_Data_Joined11, mid_dur_rptr_sex)
Overall_Data_Joined33 <- full_join(Overall_Data_Joined22, high_dur_rptr_sex)
Overall_Data_Joined44 <- full_join(Overall_Data_Joined33, freezing_dur_rptr_sex)
Overall_Data_Joined55 <- full_join(Overall_Data_Joined44, freq_high_rptr_sex)
Overall_Data_Joined_Final_sex_F0 <- full_join(Overall_Data_Joined55, latency_high_rptr_sex)

Overall_Data_Joined_Final_sex_F0
```

#Overall forest plot showing repeatabilities of control and treatment groups
```{r}

Overall_plot_F0 <- ggplot(Overall_Anxiety_Plotting_Data_F0, aes(x=Endpoint, y=r, colour=Group)) +
geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0.4, position = position_dodge(0.3), size=0.8) +
geom_point(aes(x = Endpoint, y = r), position = position_dodge(0.3), size=3)+
geom_hline(yintercept = 0, lty = "dotted") +
coord_flip()+
ylim(-0.25, 0.9)+
   theme(axis.title.y=element_blank())+
  theme_classic()+
  scale_color_manual(values=c("#000000", "#DD8D29", "#E2D200"))+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +
  theme(axis.title.y=element_blank())+
   theme(legend.position = "bottom")+
    theme(legend.title=element_blank())
 


Overall_plot_F0

ggsave(path = "../Plots", file = "Overall_plot_new.jpeg", limitsize = FALSE)
```

#Overall forest plot showing differences between males and female repeatabilities for behavioral parameters in control and treatment groups
```{r}
Sex_New_plot <-
  ggplot(Overall_Data_Joined_Final_sex_F0,
         aes(x = Endpoint, y = r, colour = Condition)) +
  geom_errorbar(
    aes(ymin = ci.lb, ymax = ci.ub),
    width = 0.4,
    position = position_dodge(0.3),
    size = 0.8
  ) +
  geom_point(aes(x = Endpoint, y = r),
             position = position_dodge(0.3),
             size = 3) +
  geom_hline(yintercept = 0, lty = "dotted") +
  coord_flip() +
  ylim(-0.4, 0.9) +
  facet_grid( ~ Tank) +
  theme(axis.title.y = element_blank()) +
  scale_color_manual(values = c("#000000", "#f8766d", "#00bfc4")) +
    theme_classic()+
  theme(
    panel.border = element_rect(
      colour = "black",
      fill = NA,
      size = 2
    ),
    axis.ticks = element_line(size = 2, color = "black"),
    axis.ticks.length = unit(0.2, "cm")
  ) +      font("xylab", size = 15) + font("xy", size = 15) + font("xy.text", size = 15) +
  theme(axis.title.y = element_blank()) +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank())

Sex_New_plot

ggsave(path = "../Plots", file = "Overall_plot_sex.jpeg", limitsize = FALSE)

```

#Generating custom designed violin plots to display raw distributions of behavioral responses
```{r}


low_dur_violin <- violin_plot_custom_hamza2(Anxiety_Joined,Anxiety_Joined$low_dur,"Time spent in low zone", "Seconds")


tot_dist_violin <- violin_plot_custom_hamza2(Anxiety_Joined, Anxiety_Joined$tot_dist, "Total distance travelled", "Distance (cm)")



mid_dur_violin <- violin_plot_custom_hamza2(Anxiety_Joined, Anxiety_Joined$mid_dur, "Time spent in mid zone", "Seconds")


high_dur_violin <- violin_plot_custom_hamza2(Anxiety_Joined, Anxiety_Joined$high_dur, "Time spent in high zone", "Seconds")


freezing_dur_violin <- violin_plot_custom_hamza2(Anxiety_Joined, log(Anxiety_Joined$freezing_dur+1), "Time spent freezing", "Seconds")


freq_violin <- violin_plot_custom_hamza2(Anxiety_Joined, Anxiety_Joined$freq_high, "Frequency of visits to high zone", "Visits")
freq_violin

latency_violin <- violin_plot_custom_hamza2(Anxiety_Joined, Anxiety_Joined$latency_high, "Latency to the high zone", "Seconds")

#Joining plots together using patchwork to create one main plot

Joined_violins_new_design <- tot_dist_violin + low_dur_violin + mid_dur_violin + high_dur_violin + freezing_dur_violin + latency_violin+freq_violin + plot_layout(ncol = 2, nrow=4)
Joined_violins_new_design

ggsave(path = "../Plots/Anxiety", file = "Behavioral responses.jpeg", limitsize = FALSE)
```

#Obtaining individual means and plotting them (tank only)
```{r}
#Total distance

individual_means_tot_dist_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(tot_dist, na.rm=TRUE))

individual_means_tot_dist_tank

indiv_tot_dist_tank <-ggplot(individual_means_tot_dist_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean distance (cm)")+
   labs(title = "Total distance travelled")+
  theme(legend.position="none")

indiv_tot_dist_tank


#Low Zone
individual_means_low_dur_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(low_dur, na.rm=TRUE))


indiv_low_dur_tank <-ggplot(individual_means_low_dur_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
   labs(title = "Time spent in low zone")+
     theme(legend.position="none")

indiv_low_dur_tank

#Mid Zone
individual_means_mid_dur_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(mid_dur, na.rm=TRUE))


indiv_mid_dur_tank <-ggplot(individual_means_mid_dur_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
   labs(title = "Time spent in mid zone")+
     theme(legend.position="none")

indiv_mid_dur_tank


#High Zone
individual_means_high_dur_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(high_dur, na.rm=TRUE))

indiv_high_dur_tank <-ggplot(individual_means_high_dur_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
   labs(title = "Time spent in high zone")+
     theme(legend.position="none")

indiv_high_dur_tank

#Freezing
individual_means_freezing_dur_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(freezing_dur, na.rm=TRUE))

indiv_freezing_dur_tank <-ggplot(individual_means_freezing_dur_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
   labs(title = "Time spent freezing")+
     theme(legend.position="none")

indiv_freezing_dur_tank


#Latency high


individual_means_latency_high_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(latency_high, na.rm=TRUE))


indiv_latency_high_tank <-ggplot(individual_means_latency_high_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean latency (seconds)")+
   labs(title = "Latency to high zone")+
     theme(legend.position="none")

indiv_latency_high_tank

#Entries to high
individual_means_entries_tank <- Anxiety_Joined %>%
    group_by(Fish_ID, Group) %>%
    dplyr::summarize(Mean = mean(freq_high, na.rm=TRUE))

indiv_entries_tank <-ggplot(individual_means_entries_tank, aes(Group, Mean, fill=Group)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
 
    theme_classic()+
  scale_fill_manual(values = wes_palette("FantasticFox1", n = 2))+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean entries")+
   labs(title = "Entries into high zone")+
    theme(legend.position="none")

indiv_entries_tank


#Joining plots


Joined_violins_indiv_tank <- indiv_tot_dist_tank + indiv_low_dur_tank + indiv_mid_dur_tank + indiv_high_dur_tank + indiv_freezing_dur_tank + indiv_latency_high_tank+indiv_entries_tank + plot_layout(ncol = 2, nrow=4)

Joined_violins_indiv_tank
```

#Obtaining individual means and plotting them (sex and tank)
```{r}



#Total distance

individual_means_tot_dist <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(tot_dist, na.rm=TRUE))

individual_means_tot_dist

indiv_tot_dist <-ggplot(individual_means_tot_dist, aes(Sex, Mean, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
    theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean distance (cm)")+
  labs(title = "Total distance travelled")+
     theme(legend.position="none")

indiv_tot_dist



#Low Zone
individual_means_low <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(low_dur, na.rm=TRUE))

indiv_low <-ggplot(individual_means_low, aes(Sex, Mean, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
   theme(legend.position="none")+
    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
   theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
  labs(title = "Time spent in low zone")+
     theme(legend.position="none")


#Mid Zone
individual_means_mid <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(mid_dur, na.rm=TRUE))

indiv_mid <-ggplot(individual_means_mid, aes(Sex, Mean, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
   theme(legend.position="none")+
    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
   theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
  labs(title = "Time spent in mid zone")+
     theme(legend.position="none")


#High Zone
individual_means_high <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(high_dur, na.rm=TRUE))

indiv_high <-ggplot(individual_means_high, aes(Sex, Mean, fill=Sex)) +
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
  theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
  labs(title = "Time spent in high zone")+
     theme(legend.position="none")



#Freezing
individual_means_freezing <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(freezing_dur, na.rm=TRUE))

indiv_freezing <-ggplot(individual_means_freezing, aes(Sex, log(Mean)+1, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
    theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean seconds")+
  labs(title = "Time spent freezing")+
     theme(legend.position="none")



#Latency to high

individual_means_latency <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(latency_high, na.rm=TRUE))

indiv_latency <-ggplot(individual_means_freezing, aes(Sex, Mean, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +

    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
      theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean latency")+
  labs(title = "Latency to high zone")+
     theme(legend.position="none")



#Entries to high
individual_means_entries <- Anxiety_Joined %>%
    group_by(Fish_ID, Sex, Group) %>%
    dplyr::summarize(Mean = mean(freq_high, na.rm=TRUE))

indiv_freq <-ggplot(individual_means_entries, aes(Sex, Mean, fill=Sex)) + 
   geom_violin(alpha = 0.1, draw_quantiles = c(0.25, 0.5, 0.75)) + 
  geom_jitter(width = 0.2, height = 0, alpha = 0.2) +
    scale_x_discrete(labels=c("female" = "Female", "male" = "Male"))+
     theme_classic()+
   facet_grid(~Group)+
  theme(axis.ticks.x=element_blank(),
       axis.title.x=element_blank())+
  labs(y="Mean entries")+
  labs(title = "Entries into high zone")+
     theme(legend.position="none")

indiv_freq

#Joining plots

Joined_violins_indiv_sex_tank <- indiv_tot_dist + indiv_low + indiv_mid + indiv_high + indiv_freezing + indiv_latency+indiv_freq + plot_layout(ncol = 2, nrow=4)

Joined_violins_indiv_sex_tank


```

#Creating data frame for within individual and between individual variances

```{r}
Overall_Data_Joined_Final_within_between <- subset(Overall_Anxiety_Data_Joined_Full_F0, Overall_Anxiety_Data_Joined_Full_F0$Group %in% c("Within-Individual Variance (Control Group)","Within-Individual Variance (Treatment Group)", "Between-Individual Variance (Control Group)", "Between-Individual Variance (Treatment Group)")) #Will be used for plotting within-and between individual variance

#Creating a new column
Overall_Data_Joined_Final_within_between$Tank <- c("Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment","Control","Control","Treatment", "Treatment")

#Renaming to plot within and between individual variances
Overall_Data_Joined_Final_within_between$Condition <- c("Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance","Between-Individual Variance", "Within-Individual Variance", "Between-Individual Variance", "Within-Individual Variance")


```

#Plot for within and between individual variance
```{r}
Overall_New_plot_within_between <- ggplot(Overall_Data_Joined_Final_within_between, aes(x=Endpoint, y=r, colour=Tank)) +
geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0.4, position = position_dodge(0.3), size=0.8) +
geom_point(aes(x = Endpoint, y = r), position = position_dodge(0.3), size=3)+
geom_hline(yintercept = 0, lty = "dotted") +
coord_flip()+
ylim(0, 1.3)+
   theme(axis.title.y=element_blank())+
  theme_classic()+
    scale_color_manual(values=c("#DD8D29", "#E2D200"))+
    theme(panel.border = element_rect(colour = "black", fill=NA, size=2),axis.ticks = element_line(size=2,color="black"),axis.ticks.length=unit(0.2,"cm"))+      font("xylab",size=15)+font("xy",size=15)+font("xy.text", size = 15) +
    theme(legend.position = "bottom")+
  theme(axis.title.y=element_blank())+
  facet_grid(~Condition)+
  labs(y = "Variance component")+
     theme(legend.title=element_blank())
 


Overall_New_plot_within_between
```


Table to display mixed model results (using stargazer)
```{r}
stargazer(Model_Tot_Dist1, Model_low_dur1, Model_mid_dur1, Model_high_dur1, Model_freezing_dur1, Model_latency_high1, Model_freq_high1, omit.stat = c("bic","aic","ll"),  covariate.labels = c("Control", "Treatment", "Male"), align = TRUE, type= "html",dep.var.labels= c("Total distance travelled", "Time spent in low zone", "Time spent in mid zone", "Time spent in high zone", "Time spent freezing", "Latency to high zone", "Entries to high zone"),dep.var.caption= "Behavioral parameters",style="all", out = "Table.html")
```
