---
title: "analysis"
output: html_document
---

### Load packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#checks for installation and loads packages
pacman::p_load(lmerTest,ggThemeAssist,rptR,lme4,readxl, plyr, magrittr, lubridate, stringr, purrr,
               sjPlot,ggplot2,lubridate,wesanderson,ggbeeswarm,emmeans,patchwork,viridis,nlme,Rmisc,ggpubr,
               stargazer)

# Load custom function to extract data 
source("../Scripts/functions_learning.R")
```

#Subset data into control and treatment groups and then by sex
```{r}
#Subsetting data by control and treatment
Learning_Control <- subset(p2cs, p2cs$set == "control") 
Learning_Treatment <- subset(p2cs, p2cs$set == "treatment") 



#Subset by sex

#Control and treatment males and females for Social stimulus
Control_Male_Learning <- subset(Learning_Control, Learning_Control$sex == "male")
Control_Female_Learning <- subset(Learning_Control, Learning_Control$sex == "female")
Treatment_Male_Learning <- subset(Learning_Treatment, Learning_Treatment$sex == "male")
Treatment_Female_Learning <- subset(Learning_Treatment, Learning_Treatment$sex == "female")
```

### MAIN ANALYSIS 
1) CHECKING NORMALITY ASSUMPTIONS WITH MIXED MODELS AND A HISTOGRAM OF RESIDUALS
2) PERFORMING REPEATABILITY ANALYSIS FOR EACH GROUP AND EXTRACTING WITHIN-AND BETWEEN-INDIVIDUAL VARIANCES AFTER A Z TRANSFORMATION
3) CALCULATING DIFFERENCES BETWEEN REPEATABILITIES
4) FINAL MIXED MODEL USING LME FUNCTION
5) CALCULATING VARIANCE DIFFERENCES BETWEEN CONTROL AND TREATMENT

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Learning <- lmer(difference ~ set + sex + (1 | fishID), data = p2cs) 
tab_model(Model_Learning)
hist(residuals(Model_Learning)) 

#Calculating repeatabilities using custom made functions
rpt_learning(Learning_Control) -> rpt_learning_control
rpt_learning_control
rpt_learning(Learning_Treatment) -> rpt_learning_treatment
rpt_learning_treatment

#Obtaining within-individual and between-individual variance 

rpt_within_learning(Learning_Control) -> within_between_learning_control
within_between_learning_control
rpt_within_learning(Learning_Treatment) -> within_between_learning_treatment
within_between_learning_treatment


#Obtaining differences between repeatabilities using custom made functions
Control_learning_boot <- unlist_rptr(rpt_learning_control)
Treatment_learning_boot <- unlist_rptr(rpt_learning_treatment) 
learning_diff <- difference_boot(Treatment_learning_boot,Control_learning_boot)  
q_learning <- quantiles_diff_boot(learning_diff) #obtaining 95% CI
m_learning <- mean(learning_diff) #Obtaining mean
m_learning
q_learning

# Calculating difference in variance between control and treatment groups
Model_Learning1 <- lme(difference ~ set + sex, random = ~ 1| fishID, data = p2cs, na.action=na.exclude) #mixed model without variance structure
summary(Model_Learning1)
Model_Learning2 <- lme(difference ~ set + sex, random = ~ 1| fishID, weights = varIdent(form=~1|set), data = p2cs, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Learning2)
anova(Model_Learning1, Model_Learning2) #calculating difference between two models to find difference in variance

#Quick Visualization
p2cs %>%
  ggplot(aes(set, difference, fill=set)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)
```

#Sex Analysis

```{r}
#Check Normality with mixed model and then histogram of residuals

Model_Learning <- lmer(difference ~ set + sex + (1 | fishID), data = p2cs) 
tab_model(Model_Learning)
hist(residuals(Model_Learning)) 

#Calculating repeatabilities using custom made functions for males (control and treatment)
rpt_learning(Control_Male_Learning) -> rpt_learning_control_male
rpt_learning_control_male
rpt_learning(Treatment_Male_Learning) -> rpt_learning_treatment_male
rpt_learning_treatment_male

#Calculating repeatabilities using custom made functions for females (control and treatment)
rpt_learning(Control_Female_Learning) -> rpt_learning_control_female
rpt_learning_control_female
rpt_learning(Treatment_Female_Learning) -> rpt_learning_treatment_female
rpt_learning_treatment_female


#Obtaining within-individual and between-individual variance for males (control and treatment)

rpt_within_learning(Control_Male_Learning) -> within_between_learning_control_male
within_between_learning_control_male
rpt_within_learning(Treatment_Male_Learning) -> within_between_learning_treatment_male
within_between_learning_treatment_male

#Obtaining within-individual and between-individual variance for females (control and treatment)

rpt_within_learning(Control_Female_Learning) -> within_between_learning_control_female
within_between_learning_control_female
rpt_within_learning(Treatment_Female_Learning) -> within_between_learning_treatment_female
within_between_learning_treatment_female


#Obtaining differences between repeatabilities of males and females in the control group
Control_learning_boot_male <- unlist_rptr(rpt_learning_control_male) #unlisting from the males
Control_learning_boot_female <- unlist_rptr(rpt_learning_control_female) #unlisting from the females
learning_diff_control <- difference_boot(Control_learning_boot_male,Control_learning_boot_female) #calculating the difference between males and females in the control group
q_learning_control <- quantiles_diff_boot(learning_diff_control) #obtaining 95% CI
m_learning_control <- mean(learning_diff_control) #Obtaining mean
m_learning_control
q_learning_control

#Obtaining differences between repeatabilities of males and females in the treatment group
Treatment_learning_boot_male <- unlist_rptr(rpt_learning_treatment_male) #unlisting from the males
Treatment_learning_boot_female <- unlist_rptr(rpt_learning_treatment_female) #unlisting from the females
learning_diff_treatment <- difference_boot(Treatment_learning_boot_female,Treatment_learning_boot_male) #calculating the difference between males and females in the control group
q_learning_treatment <- quantiles_diff_boot(learning_diff_treatment) #obtaining 95% CI
m_learning_treatment <- mean(learning_diff_treatment) #Obtaining mean
m_learning_treatment
q_learning_treatment



# Calculating difference in variance between control and treatment groups
Model_Learning1 <- lme(difference ~ set + sex, random = ~ 1| fishID, data = p2cs, na.action=na.exclude) #mixed model without variance structure
summary(Model_Learning1)
Model_Learning2 <- lme(difference ~ set + sex, random = ~ 1| fishID, weights = varIdent(form=~1|set), data = p2cs, na.action=na.exclude) #mixed model with variance structure varIdent
summary(Model_Learning2)
anova(Model_Learning1, Model_Learning2) #calculating difference between two models to find difference in variance

#Quick Visualization
p2cs %>%
  ggplot(aes(set, difference, fill=set)) +
  geom_violin(
    trim = FALSE,
    draw_quantiles = c(0.25, 0.5, 0.75), 
    alpha=0.5
  ) + 
  geom_point(position = "jitter", alpha = 0.7, size = 3)+
  facet_grid(~sex)
```
